Bayesian spectral density estimation using P-spline priors

### 2020-03-25 response.tex

\documentclass{scrartcl}
\usepackage{amsmath}
\usepackage{amsthm}
\usepackage{amssymb}
\usepackage{color}
\usepackage[english]{babel}
%\usepackage[fixlanguage]{babelbib}
\usepackage{natbib}
\usepackage[pdftex]{graphicx}
\usepackage{dsfont}
\usepackage{color}
%\usepackage{a4wide}
\usepackage[a4paper, left=3cm, right=3cm, top=2cm]{geometry}
%\usepackage{texititel}
\title{Spectral density estimation using P-spline priors}
\subtitle{Response letter to Statistical Papers}
\author{Patricio Maturana-Russel, Renate Meyer}

\newcommand{\refereeQuote}{\textit }
\newcommand{\responseDraft}{\textcolor{red}}
\newcommand{\response}{}

\parindent 0pt
\parskip 4pt

\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}
\setlength{\topmargin}{-2cm}

\pagestyle{empty}
\begin{document}
\maketitle\thispagestyle{empty}

% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------

\subsection*{Referee \#1}

\response{We would like to thank the referee for a thorough review of our paper. Below, you find a point-by-point response to your points raised. We have now carefully revised the paper taking all of your -- and the other referees' -- comments into account and hope that you will now find the paper acceptable for publication. For your convenience, all changes made are marked in red in the manuscript.}

\begin{enumerate}
\item
\refereeQuote{The authors' terminology is surprising. They compute a P-spline fit to a power spectrum, but they call it a P-spline prior. The P-spline coefficients are the parameters of the model and they have a prior.}\smallskip

\response{We have edited the manuscript and use {\em P-spline prior} only when referring to the prior but use {\em posterior distribution based on the P-spline prior} when referring to the posterior distribution or Bayesian estimate of the spectral density. However, the referee raises a subtle point here in what frequentist and Bayesian regard as unknown parameters. In our view, the unknown parameter in this model is the spectral density function. As a prior on this spectral density function, we use a mixture of P-spline distributions. The mixture weights are hyperparameters with their own hyperprior distribution.}\bigskip

\item
\refereeQuote{To get a better fit to sharp peaks in the spectrum, the authors propose an adaptive scheme for knot placement. Apparently, they forgot that the differences in the penalty must change too, to correct for the variations in the distance between knots. One solution could be to use divided differences, another to use the algorithm of Wood for a derivative-based penalty.}\smallskip

\response{Thank you very much for pointing this out. You are absolutely correct, we did use the same penalty for the unequally spaced knots as for the equidistant knots.
We have rectified this and use derivative-based penalties for the unequally spaced knots. We describe the prior specification in paragraph 4  of the section  "adaptive knots" in Chapter 3 . As third order derivative-based penalties do not make sense for cubic splines and we want to compare the results for the equally-spaced knots and adaptive knots in the simulation study, we only compare results based on first and second order difference and derivative-based penalties, respectively. Therefore we deleted the definition of the third order difference matrix in Chapter 3. }\bigskip

\item
\refereeQuote{A more principle approach is to model the logarithm of the spectrum. That can be combined with adaptive smoothing, as described by Wood and Fasiolo, or Rodrigues-Alvarez et al. R packages are available.}\smallskip

\response{It is debatable whether putting a prior on the log spectral density is more {\em principled} than putting a prior on the spectral density itself as both terms occur in the log-likelihood function (1) and thus the prior can be put on either scale. Our P-spline prior is based on the idea of approximating  a {\em density} function as a mixture of basis distributions on the unit interval.
Thus, the original scale and not the log scale is appropriate for this particular approach even though for many applications, the log-scale might be the more natural one and we cited many papers that put a prior on the log spectral density, see our paragraph 5 of the introduction. This could be an interesting avenue to pursue in future research and see whether putting a P-spline based prior on the log spectral density has advantages over putting a prior on the spectral density. We added a paragraph in the Discussion. We have now also added the references to the alternative frequentist approaches that you suggested. Thank you for pointing these out.
}\bigskip

\item
\refereeQuote{The plots of spectra and fit with logarithmic are popular in spectrum analysis, but they are a bit misleading as the fitting is done on the linear scale.}\smallskip

\response{Please see our response to the previous point. Even though we fit a mixture of B-spline densities to the normalized spectral density, it is still possible to show the fit
on the log scale. Large peaks are better visible using the log scale. We also want to have a direct comparison of our model fits in Figure 1 and figure 2 to the corresponding ones shown  in Edwards et al. (2019) so it makes sense to use the same scale.}\bigskip

\item
\refereeQuote{I took a short look at the repository. It could be made more valuable by adding the data and some example scripts.}\smallskip

\response{Data and example scripts are included in the R package {\tt psplinePsd}.}\bigskip

\item
\refereeQuote{Sunspots counts are relatively familiar, but very few people will have seen a time the light curve of S. Carinae. I propose to add a plot of (a part of) the time series.}\smallskip

\response{We have added a time series plot of the first 150 observations of the \textit{S.\ Carinae} variable star light intensities data in Figure 4}.\bigskip

\item
\refereeQuote{
The term 'P-spaced knots' is confusing in the context of P-splines, P is already used for penalties. An adaptive scheme is proposed that is not exclusive to periodograms. Simply calling them adaptive knot looks adequate to me.}\smallskip

\response{ This could indeed be confusing. We have changed 'P-spaced' to 'adaptive' knots.}\bigskip

\item
\refereeQuote{That there is no consensus on the optimal number of knots for P-splines (page 10) has a simple explanation: it is irrelevant. Ruppert's recommendations have little value.}\smallskip

\response{We see this as a rough guideline only.}\bigskip

\item
\refereeQuote{I noticed some language problems}\smallskip

\response{Thank you for pointing these out. These have been corrected.}

\end{enumerate}

\newpage
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------
% -----------------------------------------------------------------------------

\subsection*{Referee \#2}

\response{We would like to thank the referee for a thorough review of our paper. Below, you find a point-by-point response to your points raised. We have now carefully revised the paper taking all of your -- and the other referees' -- comments into account and hope that you will now find the paper acceptable for publication. For your convenience changes are marked in red in the manuscript.
} \smallskip

\begin{enumerate}
\item
\refereeQuote{The entire Section 2 is dedicated to the B-spline prior, which were already effectively introduced in Edwards et al. (2019). I would significantly reduce the length of this section.}\smallskip

\response{We have deleted the detailed description of the BspDP prior but kept the definition of the B-splines as these are required for the definition of the prior based on the  P-splines.}\bigskip

\item 
\refereeQuote{The proposed method deals with estimating one single spectral density. However, many existing paper already deal with this. Can the proposed methodology be extended to multiple or multivariate time series?}\smallskip

\response{
 This could be a
very interesting avenue for future research and we have added a paragraph in the Discussion suggesting a potential approach. However, a multivariate extension is outside the scope of this paper.}\bigskip

\item
\refereeQuote{A Metropolis step is used for v, but a data augmentation step based on Polya-Gamma auxiliary variables will allow for a full Gibbs sampler. See "Bayesian Inference for Logistic Models Using PolyaGamma Latent Variables" (2013) of Polson, Scott and Windle.}\smallskip

\response{We had already pointed this out in section "posterior computation" and had cited the paper by Polson et al. (2013).}

\end{enumerate}

\subsection*{Further Changes}

We have changed the title from {\em Spectral density estimation using P-spline priors} to {\em Bayesian spectral density estimation using P-spline priors}.\smallskip

We have added the keyword {\em Bernstein-Dirichlet process prior}.\smallskip

In the introduction, we have added references to relevant papers published in {\em Statistical Papers} that deal with the penalized spline approach for time series (these are Krivoboka et al (2006) and Wegener and Kauermann (2017)).

\end{document}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2020-03-25 pSplines.tex
changes to pSplines.tex, response.tex

As the periodogram fluctuates around the true spectral density, most  nonparametric methods for spectral density estimation hinge on  smoothing the periodogram
\begin{align*}
I_n(\lambda) = \dfrac{1}{2 \pi n} \left| \sum_{t=1}^{n} Y_t \exp \left( -i t \lambda\right)\right|^2,
\end{align*}
in one way or another, where $-\pi < \lambda \leq \pi$ is the angular frequency and $\bm{Y}=(Y_1,\ldots,Y_n)$ is a stationary time series of length $n$. The periodogram has interesting features \textcolor{red}{(***)?why is that here?}.  For instance, the periodogram evaluated at the Fourier frequencies $\lambda_i$  are asymptotically independent and follow an exponential distribution with mean $f(\lambda_i)$.  Thus, they are unbiased estimates of $f(\lambda_i)$  but not consistent \citep{Brockwell:1986}.

@@

%<<<<<<< HEAD
With the aim of reducing the computational cost of the BspDP prior approach,  we suggest to use the idea of P-splines of \cite{Eilers:1996} that \textcolor{red}{combines} a large but fixed number of  B-splines with a simple difference penalty that controls the degree of  smoothness of the spectral density. P-splines, i.e.\  equally-spaced B-splines,  have been successfully implemented for frequentist nonparametric regression but to the best of our knowledge not yet for Bayesian spectral density estimation. We suggest two novel Bayesian  approaches in this paper, both based on the Whittle likelihood and on a mixture of B-spline densities. Both approaches fix the  number of B-spline densities.  The first approach uses equally spaced knots with a P-spline prior which we define in Section III. We demonstrate that this approach yields significant savings in computational time without sacrificing accuracy over the BspDP prior approach for simple spectral structures.  The second approach has a particular  focus on spectral densities with sharp peaks. Instead of an equidistant spacing, the knots are spread based on the distribution of peaks in the periodogram. Thus the knot allocation is also data-driven as with the BspDP prior but the knots  remain fixed once allocated. This novel knot allocation scheme avoids the computational complexity of the BspDP prior.  We show that with this knot allocation scheme, the estimates of spectral densities with spikes and abrupt changes improves significantly without an increase in computing time.
=======
With the aim of reducing the computational cost of the BspDP prior approach,  we suggest to use the idea of P-splines \cite{Eilers:1996} that combine a large but fixed number of  B-splines with a simple difference penalty that controls the degree of  smoothness of the spectral density. P-splines, i.e.\  equally-spaced B-splines,  have been successfully implemented for frequentist nonparametric regression but to the best of our knowledge not yet for Bayesian spectral density estimation. We suggest 
two novel Bayesian  approaches in this paper, both based on the Whittle likelihood and on a mixture of B-spline densities. Both approaches fix the  number of B-spline densities. 
The first approach uses equally spaced knots with a P-spline prior which we define in Section III. We demonstrate that this approach yields significant savings in computational time without sacrificing accuracy over the BspDP prior approach for simple spectral structures.  The second approach has a particular  focus on spectral densities with sharp peaks. Instead of an equidistant spacing, the knots are spread based on the distribution of peaks in the periodogram. Thus the knot allocation is also data-driven as with the BspDP prior but the knots  remain fixed once
allocated. This novel knot allocation scheme avoids the computational complexity of the BspDP prior.  We show that with this knot allocation scheme, the estimates of spectral densities with spikes and abrupt changes improves significantly without an increase in computing time.
%>>>>>>> 19c7083b8cf09264b1cfb0f5ba98e32bf3de8990

@@

In our approach, the B-spline coefficients $w_k$ are weights, so positive and sum to one. 
We therefore reparametrize to the vector $\bm{v}$ with
\begin{align*}
v_k = \log \left( \dfrac{w_k}{1-\sum_{k=1}^{K-1}w_k} \right).
\end{align*}
After some calculations, it can be shown that the weights are given by
\begin{align*}
w_k = \dfrac{e^{v_k}}{1+ \sum^{K-1}_{k=1}e^{v_k}}.
\end{align*}
The last weight is defined as $w_K = 1 - \sum_{k=1}^{K-1}w_k$, thus they all sum to 1.
Then, an indirect prior is placed on the weights via
\begin{align*}
\bm{v}|\phi&\sim\text{N}_{K-1}(\bm{0}, (\phi \bm{P})^{-1})\\
\phi|\delta &\sim \text{Gamma}(\alpha_{\phi}, \delta \beta_{\phi})\\
\delta &\sim \text{Gamma}(\alpha_{\delta}, \beta_{\delta})
\end{align*}
where $\bm{v} = (v_1,\dots,v_{K-1})^\top$ is a $K-1$ dimensional parameter vector, $\phi$ is the smoothing or penalty parameter, $\textbf{P} = \textbf{D}^\top \textbf{D} +\epsilon \textbf{I}_{K-1}$ is the penalty matrix (which is a full matrix rank matrix for any small quantity $\epsilon$, for instance, $10^{-6}$) with $\textbf{D}$ the $d^{\text{th}}$ order difference matrix ($d=1,2,\ldots, K-2)$, $\alpha_{\phi}$ and $\alpha_{\delta}$ are shape parameters, $\delta \beta_{\phi}$ and $\beta_{\delta}$ are rate parameters, and $\text{Gamma}(a,b)$ denotes a gamma distribution with mean $a/b$ and variance $a/b^2$.
We used first, second and third order difference penalties in the simulation study.
The $1^{\text{st}}$ order difference matrix \textbf{D} is defined as
\begin{align*}
\begin{bmatrix}
-1 & 1   & 0  & 0 & \cdots & & & 0 \\
0  &  -1 & 1  & 0 & \cdots & & & 0 \\
\vdots  &    & \ddots & \ddots   & &&& \vdots \\   
0 &    &    &   & \cdots & 0 &  -1 & 1 \\
\end{bmatrix}
\in \mathbb{R}^{(K-2)\times (K-1)},
\end{align*}
for the $2^{\text{nd}}$ order is
\begin{align*}
\begin{bmatrix}
1 & -2 &  1 & 0 & 0 & \cdots & & & & 0 \\
0 & 1  & -2 & 1 & 0 & \cdots & & & & 0 \\
\vdots & & \ddots & \ddots & \ddots &&&&& \vdots \\
0 & &&&& \cdots & 0 & 1 & -2 & 1 
\end{bmatrix}
\in \mathbb{R}^{(K-3)\times (K-1)},
\end{align*}
and for the $3^{\text{rd}}$ order is
\begin{align*}
\setcounter{MaxMatrixCols}{12} % to include more than 10 columns in bmatrix enviroment
\begin{bmatrix}
1 & -3 &  3 & -1 &  0 & 0 & \cdots & & & & & 0 \\
0 &  1 & -3 &  3 & -1 & 0 & \cdots & & & & & 0 \\
\vdots &    & \ddots &  \ddots & \ddots & \ddots & &  & & & & \vdots \\
0 &   &  &   &  &  & \cdots & 0 & 1 & -3 & 3 & -1  
\end{bmatrix}
\end{align*}
$\in \mathbb{R}^{(K-4)\times (K-1)}$.

@@

Our\textcolor{red}{adaptive} knot location proposal works as follow.  We calculate the periodogram and apply a square root transformation in order to have more regular magnitudes and eliminate a potential trend.  Second, we standardize these values and apply the absolute value function.  We treat this transformed periodogram as a density function $\widetilde{f}$ and calculate its distribution function $F$.  Finally, the knots are allocated according to the quantiles of the inverse distribution function of $\widetilde{f}$.  Thus, in those areas in which the periodogram has sharp and abrupt changes, our procedure will assign more knots in proportion to their magnitudes. Hereafter, we will refer to this scheme as \textcolor{red}{\em adaptive knots}.%\textit{periodogram-spaced knots} or short \textit{P-spaced knots}.
%REMARK: HOW ABOUT "PERIODOGRAM-SPACED KNOTS"	OR 'P-SPACED KNOTS'  INSTEAD OF DISTRIBUTED KNOTS?

@@

The \textcolor{red}{adaptive}  knot allocation can be regarded as an empirical Bayes prior as the data are used to specify the prior distribution.  However, only the locations of the B-splines are determined by the data, not the parameters of the prior distribution which in this case are the weights $w_k$ associated with each B-spline $b_{k,r}$.  The main criticism of an empirical Bayes approach is that the data are being used twice, once to specify the prior and then again to update the prior to the posterior. Here, the data are used only once to specify the knot locations but not again to update these through the likelihood.

@@

This dataset contains 1189 visual observations of the {\it S.\ Carinae}, a variable star in the southern hemisphere sky.  These are daily observations collected by the Royal Astronomical Society of New Zealand, which correspond to 10 day averages of light intensities over several years.  This data set has been analysed in the literature previously (see for instance \cite{Cart:1997,Huerta:1999,Kirch:2018}).  It contains 40 missing observations that in this work have been replaced by the mean, thus not affecting the general features of the data.  In addition, the data has been squared root transformed and mean centred.  {\pmr The first 150 observations are displayed in Figure~\ref{fig:carinae_data}, where the missing values are replaced by the mean.}

\begin{figure}[]
	\centering
	\includegraphics[scale=0.4,clip=true,angle=0]{carinae_data.pdf}
	\caption{{\pmr First 150 observations from the \textit{S. Carinae} data.}}
	\label{fig:carinae_data}
\end{figure}

@@

>>>>

As the periodogram fluctuates around the true spectral density, most  nonparametric methods for spectral density estimation hinge on  smoothing the periodogram
\begin{align*}
I_n(\lambda) = \dfrac{1}{2 \pi n} \left| \sum_{t=1}^{n} Y_t \exp \left( -i t \lambda\right)\right|^2,
\end{align*}
in one way or another, where $-\pi < \lambda \leq \pi$ is the angular frequency and $\bm{Y}=(Y_1,\ldots,Y_n)$ is a stationary time series of length $n$. The periodogram ordinates evaluated at the Fourier frequencies $\lambda_i$  are asymptotically independent and follow an exponential distribution with mean $f(\lambda_i)$.  Thus, they are unbiased estimates of $f(\lambda_i)$  but not consistent \citep{Brockwell:1986}.

@@

%<<<<<<< HEAD
With the aim of reducing the computational cost of the BspDP prior approach,  we suggest to use the idea of P-splines of \cite{Eilers:1996} that \textcolor{red}{combines} a large but fixed number of  B-splines with a simple difference penalty that controls the degree of  smoothness of the spectral density. P-splines, i.e.\  equally-spaced B-splines,  have been successfully implemented for frequentist nonparametric regression but to the best of our knowledge not yet for Bayesian spectral density estimation. We suggest two novel Bayesian  approaches in this paper, both based on the Whittle likelihood and on a mixture of B-spline densities. Both approaches fix the  number of B-spline densities.  The first approach uses equally spaced knots with a P-spline prior which we define in Section III. We demonstrate that this approach yields significant savings in computational time without sacrificing accuracy over the BspDP prior approach for simple spectral structures.  The second approach has a particular  focus on spectral densities with sharp peaks. Instead of an equidistant spacing, the knots are spread based on the distribution of peaks in the periodogram. Thus the knot allocation is also data-driven as with the BspDP prior but the knots  remain fixed once allocated. This novel knot allocation scheme avoids the computational complexity of the BspDP prior.  We show that with this knot allocation scheme, the estimates of spectral densities with spikes and abrupt changes improves significantly without an increase in computing time.
=======
With the aim of reducing the computational cost of the BspDP prior approach,  we suggest to use the idea of P-splines \cite{Eilers:1996} that combines a large but fixed number of  B-splines with a simple difference penalty that controls the degree of  smoothness of the spectral density. P-splines, i.e.\  equally-spaced B-splines,  have been successfully implemented for frequentist nonparametric regression but to the best of our knowledge not yet for Bayesian spectral density estimation. We suggest 
two novel Bayesian  approaches in this paper, both based on the Whittle likelihood and on a mixture of B-spline densities. Both approaches fix the  number of B-spline densities. 
The first approach uses equally spaced knots with a P-spline prior which we define in Section III. We demonstrate that this approach yields significant savings in computational time without sacrificing accuracy over the BspDP prior approach for simple spectral structures.  The second approach has a particular  focus on spectral densities with sharp peaks. Instead of an equidistant spacing, the knots are spread based on the distribution of peaks in the periodogram. Thus the knot allocation is also data-driven as with the BspDP prior but the knots  remain fixed once
allocated. This novel knot allocation scheme avoids the computational complexity of the BspDP prior.  We show that with this knot allocation scheme, the estimates of spectral densities with spikes and abrupt changes improves significantly without an increase in computing time.
%>>>>>>> 19c7083b8cf09264b1cfb0f5ba98e32bf3de8990

@@

In our approach, the B-spline coefficients $w_k$ are weights, so positive and sum to one. 
We therefore reparametrize to the vector $\bm{v}$ with
\begin{align*}
v_k = \log \left( \dfrac{w_k}{1-\sum_{k=1}^{K-1}w_k} \right).
\end{align*}
After some calculations, it can be shown that the weights are given by
\begin{align*}
w_k = \dfrac{e^{v_k}}{1+ \sum^{K-1}_{k=1}e^{v_k}}.
\end{align*}
The last weight is defined as $w_K = 1 - \sum_{k=1}^{K-1}w_k$, thus they all sum to 1.
Then, an indirect prior is placed on the weights via
\begin{align*}
\bm{v}|\phi&\sim\text{N}_{K-1}(\bm{0}, (\phi \bm{P})^{-1})\\
\phi|\delta &\sim \text{Gamma}(\alpha_{\phi}, \delta \beta_{\phi})\\
\delta &\sim \text{Gamma}(\alpha_{\delta}, \beta_{\delta})
\end{align*}
where $\bm{v} = (v_1,\dots,v_{K-1})^\top$ is a $K-1$ dimensional parameter vector, $\phi$ is the smoothing or penalty parameter, $\textbf{P} = \textbf{D}^\top \textbf{D} +\epsilon \textbf{I}_{K-1}$ is the penalty matrix (which is a full matrix rank matrix for any small quantity $\epsilon$, for instance, $10^{-6}$) with $\textbf{D}$ the $d^{\text{th}}$ order difference matrix ($d=1,2,\ldots, K-2)$, $\alpha_{\phi}$ and $\alpha_{\delta}$ are shape parameters, $\delta \beta_{\phi}$ and $\beta_{\delta}$ are rate parameters, and $\text{Gamma}(a,b)$ denotes a gamma distribution with mean $a/b$ and variance $a/b^2$.
We used \textcolor{red}{first and second}  order difference penalties in the simulation study.
The $1^{\text{st}}$ order difference matrix \textbf{D} $\in \mathbb{R}^{(K-2)\times (K-1)}$  is defined as
\begin{equation}\label{eq:D1}
%\begin{align*}
\begin{bmatrix}
-1 & 1   & 0  & 0 & \cdots & & & 0 \\
0  &  -1 & 1  & 0 & \cdots & & & 0 \\
\vdots  &    & \ddots & \ddots   & &&& \vdots \\   
0 &    &    &   & \cdots & 0 &  -1 & 1 \\
\end{bmatrix}
%\end{align*}
\end{equation}
\textcolor{red}{and} the $2^{\text{nd}}$ order difference matrix $\in \mathbb{R}^{(K-3)\times (K-1)} $ as
\begin{equation}\label{eq:D2}
%\begin{align*}
\begin{bmatrix}
1 & -2 &  1 & 0 & 0 & \cdots & & & & 0 \\
0 & 1  & -2 & 1 & 0 & \cdots & & & & 0 \\
\vdots & & \ddots & \ddots & \ddots &&&&& \vdots \\
0 & &&&& \cdots & 0 & 1 & -2 & 1 
\end{bmatrix}.
%\end{align*}
\end{equation}
%and for the $3^{\text{rd}}$ order is
%\begin{align*}
%\setcounter{MaxMatrixCols}{12} % to include more than 10 columns in bmatrix enviroment
%\begin{bmatrix}
%1 & -3 &  3 & -1 &  0 & 0 & \cdots & & & & & 0 \\
%0 &  1 & -3 &  3 & -1 & 0 & \cdots & & & & & 0 \\
%\vdots &    & \ddots &  \ddots & \ddots & \ddots & &  & & & & \vdots \\
%0 &   &  &   &  &  & \cdots & 0 & 1 & -3 & 3 & -1  
%\end{bmatrix}
%\end{align*}
%$\in \mathbb{R}^{(K-4)\times (K-1)}$.  
\textcolor{red}{The rationale for using discrete second order roughness penalties as an approximation to the usual continuous roughness measure based on the integral over the second derivatives is given
in \cite{Eilers:1996}.}

@@

Our \textcolor{red}{adaptive} knot location proposal works as follow.  We calculate the periodogram and apply a square root transformation in order to have more regular magnitudes and eliminate a potential trend.  Second, we standardize these values and apply the absolute value function.  We treat this transformed periodogram as a density function $\widetilde{f}$ and calculate its distribution function $F$.  Finally, the knots are allocated according to the quantiles of the inverse distribution function of $\widetilde{f}$.  Thus, in those areas in which the periodogram has sharp and abrupt changes, our procedure will assign more knots in proportion to their magnitudes. Hereafter, we will refer to this scheme as \textcolor{red}{\em adaptive knots}.%\textit{periodogram-spaced knots} or short \textit{P-spaced knots}.
%REMARK: HOW ABOUT "PERIODOGRAM-SPACED KNOTS"	OR 'P-SPACED KNOTS'  INSTEAD OF DISTRIBUTED KNOTS?

@@

\textcolor{red}{For non-equidistant knots, it does not make sense any longer to base the definition of the covariance matrix of the Gaussian prior  on the  difference matrices as defined in (\ref{eq:D1}) and (\ref{eq:D2}) because this is an adequate approximation of the derivative-based roughness measures -- defined as the integral of the first and second order derivatives of the P-splines -- 
for equally spaced knots only. The definition of the difference matrices could be adjusted using divided differences, but here we use the derivative-based penalties as described by \cite{WoodSimon2017Pwdb}. We make use of the implementation of the derivative-based penalty matrix  by the function {\tt bsplinepen} in the R-package {\tt fda}. This penalty matrix contains the inner products of the respective first and second order derivatives of the basis functions.}

The \textcolor{red}{adaptive}  knot allocation can be regarded as an empirical Bayes prior since the data are used to specify the prior distribution.  However, only the locations of the B-splines are determined by the data, not the parameters of the prior distribution which in this case are the weights $w_k$ associated with each B-spline $b_{k,r}$.  The main criticism of an empirical Bayes approach is that the data are being used twice, once to specify the prior and then again to update the prior to the posterior. Here, the data are used only once to specify the knot locations but not again to update these through the likelihood.

@@

This dataset contains 1189 visual observations of the {\it S.\ Carinae}, a variable star in the southern hemisphere sky.  These are daily observations collected by the Royal Astronomical Society of New Zealand, which correspond to 10 day averages of light intensities over several years.  This data set has been analysed in the literature previously (see for instance \cite{Cart:1997,Huerta:1999,Kirch:2018}).  It contains 40 missing observations that in this work have been replaced by the mean, thus not affecting the general features of the data.  In addition, the data has been squared root transformed and mean centred.  \textcolor{red}{ The first 150 observations are displayed in Figure~\ref{fig:carinae_data}, where the missing values are replaced by the mean.}

\begin{figure}[]
	\centering
	\includegraphics[scale=0.4,clip=true,angle=0]{carinae_data.pdf}
	\caption{ \textcolor{red}{First 150 observations of the \textit{S. Carinae} data.}}
	\label{fig:carinae_data}
\end{figure}

@@

\textcolor{red}{As already reviewed in the introduction, many Bayesian nonparametric approaches to spectral density estimation propose to put a prior on the log-spectral density. This could be easily implemented by modifying (\ref{eq:ps_prior}) to
 \[ \log f(\pi \omega)=\sum_{k=1}^K v_k b_{k,r}(\omega,{\bm \xi})\]
and it could be interesting to examine for what class of spectral densities this prior specification would yield better posterior inference. }
